---
title: "Assignment 8 - Iteration"
author: "Md Ariful Islam Sohag"  
format:
  html:
    code-fold: true 
    embed-resources: true
    toc: true
    number-sections: true
    theme: cerulean
---

# Goal of this assignment  
The goal of this assignment is for you to **apply different iteration concepts** learned in class to a new data set.  

In specific, you will be asked to:  
  - create a function to automate plot creation  
  - apply this function to different parts of a dataset through the use of the map function.  

# Instructions  
  - Move this script into the `code` subfolder of your `08_iteration` project  
  - Move the **wheat_nk_balkh_rm.csv** data set into the `data` subfolder  
  - On this script, fill your name under the `title` section of the YAML  
  - On this script, you will be asked to:  
    - Import the raw soybeans data set used in the `02_wrangling` project  
    - Create a function to automate the creation of boxplots  
    - Create a map workflow to apply your function to different locations in the data set  
    
# Code  
Hereafter is where you will develop your code.  
Remember to load any necessary packages and the data.    

```{r setup}
#| message: false
#| warning: false

library(tidyverse)  # Includes dplyr, ggplot2, and purrr
library(readr)      # For reading CSV files
library(readxl) # to read excel files
library(janitor) # to clean data

```

# Importing the data.  
```{r}
#| message: false

soyk <- readxl::read_excel("../data/01_soybeans.xlsx")

soyk
```
# Data Wrangling

In this chunk, I want to have clean names for the colums. ALso I changed the clomun name for site only with the site name.
```{r}
soyk_w <- soyk %>% 
  clean_names() %>%
  rename(k_rate = k_rate_lbac,
         tifton = tifton_k_pct,
         midville = midville_k_pct,
         watkinsville = watkinsville_k_pct,
         macon = macon_k_pct)

soyk_w
```

#EDA
I want to look at the data and have an idea about it.
```{r}
summary(soyk_w)
```



## Q1 - Create a function  
Here, you are asked to create a function.  
The goal of this function is to create a boxplot of K leaf concentration as a function of K rates.    
Name the function `myplot`.  
The function inputs are:  
  - df: the data set containing the columns needed for plotting  
  - x: the column name inside df to be plotted on the x axis  
  - y: the column name inside df to be plotted on the y axis  

Once you create the function, make sure it works by applying it to one of the locations where K leaf concentration was collected.  


Before creating the function, I want to make a pivot longer for each site and look at the range of the K concentration by using density function
```{r}
soyk_w %>%
  pivot_longer(cols = tifton:macon) %>%
  arrange(name) %>%
  ggplot(aes(x=value))+
  geom_density()+
  facet_wrap(~name, scales = "free")
```


Now I can create the function
```{r}
# Function to create boxplot of yield as a function of K rates
myplot <- function(df, x, y) {
  ggplot(df, aes(x = factor(.data[[x]]), y = .data[[y]], group = factor(.data[[x]]))) +
    geom_boxplot(fill = "Darkgreen") +
    labs(
      title = paste("Boxplot of", y, "as a function of", x),
      x = str_to_title(gsub("_", " ", x)),
      y = str_to_title(gsub("_", " ", y))
    ) +
    theme_minimal() +
    theme(plot.title = element_text(hjust = 0.5))
}
```

Now, I want to check the validity of the function for one site
```{r}
# Test the function with one location (tifton)
test_plot <- myplot(soyk_w,"k_rate", "tifton")

test_plot
```

## Q2 - Iterate over locations  
On the step above you created a function to create boxplot for one location (one column in your original data set).  

Now, you are asked to apply this function to each location in the data set.  
For that, use one of the functions in the `map` family from the purr package.  
When making your plots, make sure to add a title to represent which location is represented in each plot.  

Before doing the Iteration for all the site, I want to create a vactor for all K percentage column
```{r}
# Create a vector of all K percentage columns
k_pct_cols <- c("tifton", "midville", "watkinsville", "macon")
```

In this chunk I will use map function to iterate over all the location
```{r}
# Use map to apply the myplot function to each location
k_plots <- map(k_pct_cols, ~ myplot(soyk_w, "k_rate", .x)) 

k_plots
```

# Submitting your work  
Once you have developed all the code and answers, make sure to Render this quarto file.  

**Notes on rendering**:  

- Make sure to render your work and inspect how the final html look like.  
- If it does not look professional for whatever reason, then fix the issue, re-render it, recheck.  
- Only send me your work once your html file looks professional.  
  - **DO NOT** delete the file's heading levels (# and ##). They set up the proper heading 1 and 2 levels, and I use them to guide my grading.  
  - If a given chunk is also outputting warnings or messages, inhibit this behavior by changing the chunk options `message` and `warning` to `FALSE` (I'll demo this in a moment).  
  
  - If, after rendered, 2 lines of text are connected and you wish to "break line" between them, add 2 extra spaces after the first one (I'lld demo this in a moment).  

After rendering, an .html file will be created on your `code` folder.  

Rename this file to `Assignment-08-iteration-LASTNAME.html`.    

For ex., mine would be `Assignment-08-iteration-Bastos.html`.

Submit your work by uploading the **html** file to **eLC Assigment #8 - Iteration** by Mar 18 11:59 pm.  
  




